\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-20 pldi/draft.tex
First pass on section 5.2

\noindent
\TODO{Problem: Pipeline width shrinks after pure commands. Solution:
  Split node that resplits its input to multiple files in sequence (to
  preserve the model semantics).}

>>>>

As described in \Cref{ir:transformations}, \sys transformations
inserts \ttt{split} nodes to expose parallelism in cases where a
parallelizable node only has one input. The \sys \todo{backend} offers
two options for implementing this split node, to satisfy the inherent
tension between task-based parallelism and knowledge of the number of
lines in the \ttt{split} input. In the general case, the number of
lines of a specific edge is not known a-priori (due to commands that
remove or add new lines), and so \sys provides an automatic split that
first counts the number of lines, and then splits its input to the
desired number of outputs. If however, the user knows the number of
lines at the split insertion edge, they can provide it to \sys, that
then uses it to \ttt{split} without having to block and read its whole
input first. \sys also inserts eager relay nodes after all but the
last output of split in order to address the laziness issue that was
described before.

%% \noindent
%% \TODO{Problem: Pipeline width shrinks after pure commands. Solution:
%%   Split node that resplits its input to multiple files in sequence (to
%%   preserve the model semantics).}
